Spatial Analysis

### 2021-06-28 Scripts/spatial_analisis.Rmd
Removed Pennsylvania from the analysis

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
    theme: darkly
---

@@

States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina","pennsylvania")

@@

@@

# Looks good
state_sf %>%
  st_transform(4326) %>% # to match shape
  st_set_crs(4326) %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
  ggplot() +
  geom_sf(aes(color = state))+
  # geom_sf(data = eez_sf, aes(),fill =NA) +
  # ggplot()+
  geom_tile(data = ne_grid,
            aes(
              x = lon,
              y = lat
            ),
            alpha = 0.2
  ) +
  scale_color_manual(values = state_pallet)

@@

# Get the overlapping segments
grid_eez_sf <- st_intersection(grid_sf,eez_sf)

# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

@@

>>>>

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  # html_document
  html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
    theme: darkly
---

@@

States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")

@@

# Create specific state pallet from our friend Wes Andersson
state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 5, name = "Darjeeling2"),
                               wes_palette(n = 3, name = "Royal1")
                  )

@@

# Looks good
state_sf %>%
  st_transform(4326) %>% # to match shape
  st_set_crs(4326) %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
  ggplot() +
  geom_sf(aes(color = state))+
  # geom_sf(data = eez_sf, aes(),fill =NA) +
  # ggplot()+
  geom_tile(data = ne_grid,
            aes(
              x = lon,
              y = lat
            ),
            alpha = 0.2
  ) +
  scale_color_manual(values = state_pallet) +
  theme_bw()

@@

# Get the overlapping segments 
# NOTE: Takes some gooooood time
grid_eez_sf <- st_intersection(grid_sf,eez_sf)

write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

@@

# Remove Pennsylvania from sf
grid_eez_df <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>% 
  filter(state != "pennsylvania")

# Make sure no Penn.
unique(grid_eez_df$state)

# over write sf
write_sf(grid_eez_df, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

#Make sure of things

grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")

unique(grid_eez_sf$state)

# DONE!
